---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    notebook_metadata_filter: -jupytext.text_representation.jupytext_version
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# ABLE Sentinel mooring file conversion

This R script converts the raw data into a CF compliant netcdf file and does the following basic processing steps:

* Removing times when the instruments were out of the water
* Removing acoustic returns from above the surface and below the bottom

```{r}
library(oce)
source("ncwrite.R")
save_dir <- "../proc/ABLE_sentinel_mooring"
```

# Common parameters

Common to all instruments

```{r}
lat <- 56.8370392
lon <- -132.3574123
dec <- 19.32  # magnetic declination
```

# Sentinel V

## Checks

Basic info

```{r}
file <- "~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/ABLE_Sentinel/ADCP/LeConte S-ABLE Sept2018 20180901T233454.pd0"
ori <- "upward"  # orientation
```

Load data

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon)
adp <- oceSetMetadata(adp, 'orientation', ori)
```

```{r}
summary(adp)
```

### Find time in water

```{r}
plot(adp, which="pressure")
```

Indicates the pressure cut should be 125 dbar.

```{r}
pmin <- 130
adp <- subset(adp, pressure > pmin)
```

```{r}
plot(adp, which="pressure")
```

```{r}
i0 <- 1
i1 <- 100
# N <- 670412
plot(adp[['time']][i0:i1], adp[['temperature']][i0:i1])
plot(adp[['time']][i0:i1], adp[['pitch']][i0:i1])
plot(adp[['time']][i0:i1], adp[['roll']][i0:i1])
plot(adp[['time']][i0:i1], adp[['pressure']][i0:i1])
```

```{r}
adp[['time']][1]
```

```{r}
tail(adp[['time']], n=1)
```

```{r}
from <- as.POSIXct("2018-09-02 01:16:45", tz="UTC")
from1 <- as.POSIXct("2018-09-02 01:20:00", tz="UTC")

plot(subset(subset(adp, time > from), time < from1), which="pressure")
```

```{r}
to <- as.POSIXct("2018-09-15 22:15:30", tz="UTC")
to1 <- as.POSIXct("2018-09-15 22:14:00", tz="UTC")

plot(subset(subset(adp, time < to), time > to1), which="pressure")
```

### Find bottom cut off

```{r}
plot(subset(adp, distance < 145), which=5)
```

## Save

Parameters

```{r}
from <- as.POSIXct("2018-09-02 01:16:45", tz="UTC")
to <- as.POSIXct("2018-09-15 22:15:30", tz="UTC")
dmax <- 145  # Max distance
```

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon, from = from, to = to)
adp <- oceSetMetadata(adp, 'orientation', ori)
adp <- subset(adp, distance < dmax)
```

Coordinate transformations

```{r}
# Convert to xyz coordinates
xyz <- beamToXyz(adp)

xyzv <- xyz
# Extract vertical beam to new object
xyzv[["v"]][,,3] <- xyz[["vv"]]

enu <- xyzToEnu(xyz, declination = dec)
# Apply rotation with 5th beam
enuv <- xyzToEnu(xyzv, declination = dec)
# Put rotated 5th beam back into original object
enu[["vv"]] <- enuv[["v"]][,,3]
```

```{r}
SN <- enu[['serialNumber']]
```

```{r}
SN
```

```{r}
adp_write(enu, file.path(save_dir, "sentinelV_SN17312.nc"), overwrite=TRUE)
```

# CTD sensors

```{r}
# Microcat
file <- "~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/ABLE_Sentinel/SBE/SBE37SM-RS232_03707818_2018_09_18.cnv"

ctd <- read.ctd(path.expand(file))

ctd[['time']] <- ctd[['time']]
ctd[['latitude']] <- lat
ctd[['longitude']] <- lon

ctd <- subset(subset(ctd, time > from), time < to)

save_name <- paste("SBE37SM_SN", ctd[['serialNumberTemperature']], ".nc", sep="")
write(save_name, stdout())

write_moored_ctd(ctd, file.path(save_dir, save_name), overwrite=TRUE)
```

# Turbidity sensor

```{r}
# Turbidity sensor
file <- "~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/ABLE_Sentinel/RBR_Virtuoso_Turbidity/054311_20180915_2116.rsk"

rsk <- read.rsk(path.expand(file), from = from, to = to)

rsk@metadata["latitude"] <- lat
rsk@metadata["longitude"] <- lon
rsk@metadata["model"] <- substr(rsk[['model']], 1, 11)  # Get rid of the silly unicode character... 

save_name <- paste(rsk[['model']], "_SN", rsk[['serialNumber']], ".nc", sep="")
write(save_name, stdout())

write_moored_rsk(rsk, file.path(save_dir, save_name), overwrite=TRUE)
```

# Copy additional metadata

```{r}
# Metadata
file.copy(path.expand("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/recovery_notes.txt"), save_dir)
# Diagrams
file.copy(path.expand("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/mooring_diagrams/ABLE_S.jpg"), save_dir)
```

```{r}
txt <- "# ABLE sentinel mooring

## Instrument layout

Also see diagram in ABLE_S.jpg

   |-----------------+--------------------|
   | Reference Point | Description        |
   |-----------------+--------------------|
   |               1 | Microcat 7871      |
   |-----------------+--------------------|

   |-------------+---------+----------+--------|
   | Type        | Pos (m) | Ref. Pt. | Serial |
   |-------------+---------+----------+--------|
   | Sentinel V  |   3.75  |        1 |  17312 |
   | Microcat    |      0  |        1 |   7871 |
   |-------------+---------+----------+--------|

# Notes
## Sentinel V ADCP
  - Clock 12.6 seconds behind UTC on recovery

"
writeLines(txt, file.path(save_dir, "mooring_description.txt"))
```
