---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    notebook_metadata_filter: -jupytext.text_representation.jupytext_version
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Downstream deep mooring file conversion

This R script converts the raw data into a CF compliant netcdf file and does the following basic processing steps:

* Removing times when the instruments were out of the water
* Removing acoustic returns from above the surface and below the bottom

```{r}
library(oce)
source("ncwrite.R")
save_dir <- "../proc/downstream_deep_mooring"
```

# Common parameters

Common to all instruments

```{r}
lat <- 56.83596667
lon <- -132.3616833
dec <- 19.32  # magnetic declination
```

# Downward looking Workhorse

## Checks

Basic info

```{r}
file <- "~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/Downstream_Deep/ADCP/SN_54000.000"
ori <- "downward"  # orientation
```

Load data

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon)
adp <- oceSetMetadata(adp, 'orientation', ori)
```

```{r}
summary(adp)
```

### Find time in water

```{r}
plot(adp, which="pressure")
```

Indicates the pressure cut should be 80 dbar.

```{r}
pmin <- 80
adp <- subset(adp, pressure > pmin)
```

```{r}
plot(adp, which="pressure")
```

```{r}
i0 <- 1
i1 <- 100
# N <- 670412
plot(adp[['time']][i0:i1], adp[['temperature']][i0:i1])
plot(adp[['time']][i0:i1], adp[['pitch']][i0:i1])
plot(adp[['time']][i0:i1], adp[['roll']][i0:i1])
plot(adp[['time']][i0:i1], adp[['pressure']][i0:i1])
```

```{r}
adp[['time']][1]
```

```{r}
tail(adp[['time']], n=1)
```

```{r}
from <- as.POSIXct("2018-09-03 02:17:00", tz="UTC")
from1 <- as.POSIXct("2018-09-03 02:20:54", tz="UTC")

plot(subset(subset(adp, time > from), time < from1), which="pressure")
```

```{r}
to <- as.POSIXct("2018-09-16 16:10:15", tz="UTC")
to1 <- as.POSIXct("2018-09-16 16:00:00", tz="UTC")

plot(subset(subset(adp, time < to), time > to1), which="pressure")
```

### Find bottom cut off

```{r}
plot(subset(adp, distance < 105), which=5:8)
```

## Save

Parameters

```{r}
from <- as.POSIXct("2018-09-03 02:17:00", tz="UTC")
to <- as.POSIXct("2018-09-16 16:10:15", tz="UTC")
dmax <- 105  # Max distance
```

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon, from = from, to = to)
adp <- oceSetMetadata(adp, 'orientation', ori)
adp <- subset(adp, distance < dmax)
```

Coordinate transformations

```{r}
xyz <- beamToXyz(adp)
enu <- xyzToEnu(xyz, declination = dec)
```

```{r}
SN <- enu[['serialNumber']]
```

```{r}
SN
```

```{r}
adp_write(enu, file.path(save_dir, "workhorse300_downward_SN00054.nc"), overwrite=TRUE)
```

# Upward looking Workhorse

## Checks

```{r}
file <- "~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/Downstream_Deep/ADCP/15645000.000"
ori <- "upward"  # orientation
```

Load data

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon, from = from, to = to)
adp <- oceSetMetadata(adp, 'orientation', ori)
```

### Find surface cut off

```{r}
plot(subset(adp, distance < 90), which=5:8)
```

## Save

```{r}
dmax <- 90  # Max distance
```

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon, from = from, to = to)
adp <- oceSetMetadata(adp, 'orientation', ori)
adp <- subset(adp, distance < dmax)
```

```{r}
xyz <- beamToXyz(adp)
enu <- xyzToEnu(xyz, declination = dec)
```

```{r}
SN <- enu[['serialNumber']]
```

```{r}
SN
```

```{r}
adp_write(enu, file.path(save_dir, "workhorse300_upward_SN15645.nc"), overwrite=TRUE)
```

# CTD sensors

```{r}
files <- Sys.glob("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/Downstream_Deep/SBE/SBE37SM*.cnv")
```

```{r}
for (file in files) {
    ctd <- read.ctd(path.expand(file))
    
    ctd[['time']] <- ctd[['time']]
    ctd[['latitude']] <- lat
    ctd[['longitude']] <- lon
    
    ctd <- subset(subset(ctd, time > from), time < to)
    
    save_name <- paste("SBE37SM_SN", ctd[['serialNumberTemperature']], ".nc", sep="")
    write(save_name, stdout())
    
    write_moored_ctd(ctd, file.path(save_dir, save_name), overwrite=TRUE)
} 
```

# T sensors

```{r}
files <- Sys.glob("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/Downstream_Deep/RBR_Solo/*.rsk")
```

```{r}
for (file in files) {
    rsk <- read.rsk(path.expand(file), from = from, to = to)
    
    rsk@metadata["latitude"] <- lat
    rsk@metadata["longitude"] <- lon
    
    save_name <- paste(rsk[['model']], "_SN", rsk[['serialNumber']], ".nc", sep="")
    write(save_name, stdout())
    
    write_moored_rsk(rsk, file.path(save_dir, save_name), overwrite=TRUE)
} 
```

# Copy additional metadata

```{r}
# Metadata
file.copy(path.expand("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/recovery_notes.txt"), save_dir)
# Diagrams
file.copy(Sys.glob("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/mooring_diagrams/downstream*.jpg"), save_dir)
```

```{r}
txt <- "# Downstream deep mooring

## Instrument layout

Also see diagram in jpg files starting with downstream_

   |-----------------+--------------------|
   | Reference Point | Description        |
   |-----------------+--------------------|
   |               1 | Bottom of 50m line |
   |               2 | Bottom of 78m line |
   |-----------------+--------------------|

   |-------------+---------+----------+--------|
   | Type        | Pos (m) | Ref. Pt. | Serial |
   |-------------+---------+----------+--------|
   | Microcat    |      48 |          |  10552 |
   | RBR Solo    |      45 |        1 | 100028 |
   | RBR Solo    |      40 |        1 | 100027 |
   | RBR Solo    |      30 |        1 | 100024 |
   | RBR Solo    |      20 |        1 | 100022 |
   | RBR Solo    |      10 |        1 | 100020 |
   | RBR Solo    |       5 |        1 | 100021 |
   |-------------+---------+----------+--------|
   | ADCP (up)   |         |          |  15645 |
   | Microcat    |         |          |  10551 |
   | ADCP (down) |         |          |     54 |
   | RBR Solo    |         |          | 100320 |
   |-------------+---------+----------+--------|
   | RBR Solo    |      70 |        2 | 101189 |
   | RBR Solo    |      60 |        2 | 101191 |
   | RBR Solo    |      50 |        2 | 101193 |
   | RBR Solo    |      40 |        2 | 101194 |
   | Microcat    |         |          |  07819 |
   | RBR Solo    |      30 |        2 | 101190 |
   | RBR Solo    |      20 |        2 | 101197 |
   | RBR Solo    |      10 |        2 | 101196 |
   | RBR Solo    |       5 |        2 | 101192 |
   | RBR Solo    |       1 |        2 | 101195 |
   |-------------+---------+----------+--------|
   | Microcat    |       0 |          |  10553 |
   | RBR Solo    |         |          | 101180 |
   |-------------+---------+----------+--------|

# Notes
## ADCP 54
   - At 2018-09-17 15:59:20, ADCP clock read 2018-09-17 15:59:34
## ADCP 15645
   - At 2018-09-17 00:53:15 ADCP clock read 2018-09-17 00:52:58
## RBR Solos
   - 100022: At 2018-09-18 00:55:13 solo clock read 00:55:11
   - 100020: At 2018-09-18 01:07:08 solo clock read 01:07:06
   - 100028: At 2018-09-18 01:10:17 solo clock read 01:10:17
   - 100027: At 2018-09-18 01:25:47 solo clock read 01:25:46
   - 100021: At 2018-09-18 01:28:38 solo clock read 01:28:37
   - 101193: At 2018-09-18 01:31:18 solo clock read 01:31:18
   - 101197: At 2018-09-18 01:36:49 solo clock read 01:36:50
   - 100024: At 2018-09-18 01:39:10 solo clock read 01:39:12
   - 101196: At 2018-09-18 01:41:58 solo clock read 01:41:57
   - 101194: At 2018-09-18 01:44:10 solo clock read 01:44:11
   - 100320: At 2018-09-18 01:47:13 solo clock read 01:47:12
   - 101190: At 2018-09-18 02:07:52 solo clock read 02:07:53
   - 101191: At 2018-09-18 02:10:56 solo clock read 02:10:56
   - 101180: At 2018-09-18 02:13:54 solo clock read 02:13:53
   - 101189: At 2018-09-18 02:16:18 solo clock read 02:16:17
   - 101192: At 2018-09-18 02:25:01 solo clock read 02:25:02
   - 101195: At 2018-09-18 02:28:01 solo clock read 02:28:02

## Microcats
   - Different serial number for one of the microcats on recovered compared to
     mooring diagram. Microcat located on 78m wire rope. It looks like one digit
     was switched and last 4 were not included. Written down as 56016. Serial
     number of instrument taken off:37SM56061-7819
"
writeLines(txt, file.path(save_dir, "mooring_description.txt"))
```
