---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    notebook_metadata_filter: -jupytext.text_representation.jupytext_version
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Downstream deep mooring file conversion

This R script converts the raw data into a CF compliant netcdf file and does the following basic processing steps:

* Removing times when the instruments were out of the water
* Removing acoustic returns from above the surface and below the bottom

```{r}
library(oce)
source("ncwrite.R")
save_dir <- "../proc/downstream_deep_mooring"
```

# Common parameters

Common to all instruments

```{r}
lat <- 56.83596667
lon <- -132.3616833
dec <- 19.32  # magnetic declination
```

# Downward looking Workhorse

## Checks

Basic info

```{r}
file <- "~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/Downstream_Deep/ADCP/SN_54000.000"
ori <- "downward"  # orientation
```

Load data

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon)
adp <- oceSetMetadata(adp, 'orientation', ori)
```

```{r}
summary(adp)
```

### Find time in water

```{r}
plot(adp, which="pressure")
```

Indicates the pressure cut should be 80 dbar.

```{r}
pmin <- 80
adp <- subset(adp, pressure > pmin)
```

```{r}
plot(adp, which="pressure")
```

```{r}
i0 <- 1
i1 <- 100
# N <- 670412
plot(adp[['time']][i0:i1], adp[['temperature']][i0:i1])
plot(adp[['time']][i0:i1], adp[['pitch']][i0:i1])
plot(adp[['time']][i0:i1], adp[['roll']][i0:i1])
plot(adp[['time']][i0:i1], adp[['pressure']][i0:i1])
```

```{r}
adp[['time']][1]
```

```{r}
tail(adp[['time']], n=1)
```

```{r}
from <- as.POSIXct("2018-09-03 02:17:00", tz="UTC")
from1 <- as.POSIXct("2018-09-03 02:20:54", tz="UTC")

plot(subset(subset(adp, time > from), time < from1), which="pressure")
```

```{r}
to <- as.POSIXct("2018-09-16 16:10:15", tz="UTC")
to1 <- as.POSIXct("2018-09-16 16:00:00", tz="UTC")

plot(subset(subset(adp, time < to), time > to1), which="pressure")
```

### Find bottom cut off

```{r}
plot(subset(adp, distance < 105), which=5:8)
```

## Save

Parameters

```{r}
from <- as.POSIXct("2018-09-03 02:17:00", tz="UTC")
to <- as.POSIXct("2018-09-16 16:10:15", tz="UTC")
dmax <- 105  # Max distance
```

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon, from = from, to = to)
adp <- oceSetMetadata(adp, 'orientation', ori)
adp <- subset(adp, distance < dmax)
```

Coordinate transformations

```{r}
xyz <- beamToXyz(adp)
enu <- xyzToEnu(xyz, declination = dec)
```

```{r}
SN <- enu[['serialNumber']]
```

```{r}
SN
```

```{r}
adp_write(enu, file.path(save_dir, "workhorse300_downward_SN00054.nc"), overwrite=TRUE)
```

# Upward looking Workhorse

## Checks

```{r}
file <- "~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/Downstream_Deep/ADCP/15645000.000"
ori <- "upward"  # orientation
```

Load data

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon, from = from, to = to)
adp <- oceSetMetadata(adp, 'orientation', ori)
```

### Find surface cut off

```{r}
plot(subset(adp, distance < 90), which=5:8)
```

## Save

```{r}
dmax <- 90  # Max distance
```

```{r}
file <- path.expand(file)
adp <- read.adp(file, latitude = lat, longitude = lon, from = from, to = to)
adp <- oceSetMetadata(adp, 'orientation', ori)
adp <- subset(adp, distance < dmax)
```

```{r}
xyz <- beamToXyz(adp)
enu <- xyzToEnu(xyz, declination = dec)
```

```{r}
SN <- enu[['serialNumber']]
```

```{r}
SN
```

```{r}
adp_write(enu, file.path(save_dir, "workhorse300_upward_SN15645.nc"), overwrite=TRUE)
```

# CTD sensors

```{r}
files <- Sys.glob("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/Downstream_Deep/SBE/SBE37SM*.cnv")
```

```{r}
for (file in files) {
    ctd <- read.ctd(path.expand(file))
    
    ctd[['time']] <- ctd[['time']]
    ctd[['latitude']] <- lat
    ctd[['longitude']] <- lon
    
    ctd <- subset(subset(ctd, time > from), time < to)
    
    save_name <- paste("SBE37SM_", ctd[['serialNumberTemperature']], ".nc", sep="")
    write(save_name, stdout())
    
    write_moored_ctd(ctd, file.path(save_dir, save_name), overwrite=TRUE)
} 
```

# T sensors

```{r}
files <- Sys.glob("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/Downstream_Deep/RBR_Solo/*.rsk")
```

```{r}
for (file in files) {
    rsk <- read.rsk(path.expand(file), from = from, to = to)
    
    rsk@metadata["latitude"] <- lat
    rsk@metadata["longitude"] <- lon
    
    save_name <- paste(rsk[['model']], "_", rsk[['serialNumber']], ".nc", sep="")
    write(save_name, stdout())
    
    write_moored_rsk(rsk, file.path("../proc/downstream_deep_mooring", save_name), overwrite=TRUE)
} 
```

# Copy additional metadata

```{r}
# Metadata
file.copy(path.expand("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/recovery_notes.txt"), save_dir)
# Diagrams
file.copy(Sys.glob("~/Dropbox/LeConte/Data/ocean/september2018/raw/moorings/mooring_diagrams/downstream*.jpg"), save_dir)
```
